---
title: 'Building information: Accessible Display'
author: 'Accessibility Mapping Project'
date: '`r format(Sys.Date(), format="%B %d, %Y")`'
lang: 'en'
output: 
  html_document:
    keep_md: true
    self_contained: false
params: 
  output_dir: 'output'
---

<!-- This can be viewed, e.g., at 
https://rawgit.com/publicus/upenn-accessible-spaces-dynamic-report/master/Example.html
-->

# TODO

- Finish writing the document
- Only retaining the raw HTML for the body section of the document

### Stretch goals

- Using WordPress API to update a post?
  - E.g., `http://web.sas.upenn.edu/access-map/wp-json/wp/v2/pages/` works for *reading* pages Not sure about updating pages yet, though a `PUT` command should work for it.

```{r setup, include=FALSE}
library('dplyr')
library('glue')
library('httr')
library('jsonlite')
library('knitr')
library('readr')

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = TRUE)
knitr::opts_chunk$set(results = 'asis')
```

```{r load data}
dataset <- readr::read_csv("Building-Interiors-7-4-18_fixed.csv")
```

## Summary

We have compiled data on `r dataset %>% nrow()` buildings in this document. Below, you will find information on each building individually.


```{r loop through buildings}
say <- function(..., space_separator = '\n\n') {
  cat(space_separator, ..., sep = '', collapse = '')
}

talk_about_building_information <- function(
  row_of_data,
  name_of_information,
  binary_column_name,
  details_column_name
) {
  say(
    glue::glue('- {name_of_information}: '),
    if (
      is.na(row %>% pull(!!as.name(binary_column_name)))
    ) {
      paste('(Unknown)')
    } else if (
      row %>% pull(!!as.name(binary_column_name)) == 'yes'
    ) {
      paste(
        glue::glue('There *is* {name_of_information}:'),
        row %>% pull(!!as.name(details_column_name))
      )
    } else {
      glue::glue('There is *not* signage about {name_of_information} in this building.')
    }
  )
}

for (row_number in 1:nrow(dataset)) {
  row <- dataset %>% slice(row_number)
  
  say('## Building Name: ', row %>% pull(`Building name`))
  say('### Building Information')
  
  say('- Building location (GPS coordinates): ', row %>% pull(x), ", ", row %>% pull(y))
  
  say('- Braille or tactile signage: ', row %>% pull('Braille/tactile signage?'), '; ', row %>% pull('Braille Description'))
  
  say('- Inaccessible spaces: ', row %>% pull('Inaccessible spaces'), '; ', row %>% pull('Inaccessible Spaces Description'))
  
  say('- Lighting: ', row %>% pull('How are the hallways lit?'), '; ', row %>% pull('Describe the lighting'))

  say('- Chemicals or allergens: ', row %>% pull('Chemicals and allergens?'))
  
  # TODO:
    # Inaccessible spaces: inaccess
    # If yes, describe these: inaccess_notes
    # How are the hallways lit? light_type
    # Describe the lighting: light_note
    # Chemicals and allergens? chemical
  
  say('### Building Features')
  
  say(
    '- Floors: ', row %>% pull('Number of floors'))
  
  say(
    '- Stairwells: ', row %>% pull(`Number of stairwells`))  

  say(
    '- Elevators: ', row %>% pull(`Number of elevators`))

  say(
    '- Accessible bathrooms: ', row %>% pull(`Number of accessible bathrooms`))

  say(
    '- Gender-neutral bathrooms: ', row %>% pull(`Number of gender-neutral bathrooms`))

  say(
    '- Gender-neutral accessible bathrooms: ', row %>% pull(`Gender-neutral accessible bathrooms?`))

  say(
    '- Total bathrooms: ', row %>% pull(`Total bathrooms`))

  say(
    '- Lactation spaces?: ', row %>% pull(`Are there any lactation spaces?`))

  say(
    '- Prayer or meditation spaces?: ', row %>% pull(`Are there prayer or meditation spaces?`))

   

  # TODO:
    # stairwells: stairwells
    # elevators: elevators
    # acc_bath: accessible bathrooms
    # gn_bath: gender-neutral bathrooms
    # gn_acc_bath: accessible gender-neutral bathrooms
    # total_bath: total bathrooms
    # lactation: Are there any lactation spaces? 
    # prayer: Are there prayer or meditation spaces?
  
  say('### Additional information')
  
  say(row %>% pull(`Comments and additional information`))
}  # End of for loop
```
