---
title: 'Summary of Space Accessiblity'
author: 'R Group'
date: '`r format(Sys.Date(), format="%B %d, %Y")`'
output: 
  html_document:
    keep_md: true
    self_contained: false
params: 
  output_dir: 'output'
---

# TODO

- Finish writing the document
- Only retaining the raw HTML for the body section of the document

## Stretch goals

- Document language
- API Access to ArcGIS dataset

### Secondary stretch goals

- Using WordPress API to update a post?
  - E.g., `http://web.sas.upenn.edu/access-map/wp-json/wp/v2/pages/` works for *reading* pages Not sure about updating pages yet, though a `PUT` command should work for it.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = TRUE)
knitr::opts_chunk$set(results = 'asis')

library('dplyr')
library('httr')
library('jsonlite')
library('readr')
```

```{r load data}
dataset <- readr::read_csv("building_inter_4-2-18_FIXED_FIRST_STRING.csv")
```

```{r include=TRUE}
cat("Test")
```

## Summary

We have compiled data on `r dataset %>% nrow()` buildings in this document. Below, you will find information on each building individually.

```{r how many inacessible spaces are there}
inaccessible_spaces <- dataset %>% filter(`Inaccessible spaces` == 'yes')
```

Overall, `r inaccessible_spaces %>% nrow()` (that is, `r ((inaccessible_spaces %>% nrow()) / (dataset %>% nrow()) * 100) %>% round(2)`%) of the `r dataset %>% nrow()` buildings in the dataset contain inaccessible spaces.

```{r loop through buildings}
# base_attachment_url <- 'https://services3.arcgis.com/9nfxWATFamVUTTGb/arcgis/rest/services/service_12179aa8762647dba17ff539184807a7/FeatureServer/0/'

say <- function(..., space_separator = '\n\n') {
  cat(space_separator, ..., sep = '', collapse = '')
}

for (row_number in 1:nrow(dataset)) {
  row <- dataset %>% slice(row_number)
  
  say('## Building Name: ', row %>% pull(`Building name`))
  say('### Building Information')
  
  say('- Building location (GPS coordinates): ', row %>% pull(x), ", ", row %>% pull(y))
  
  say(
    '- Braille/tactile signage: ',
    if(
      !is.na(row %>% pull(`Braille/tactile signage?`)) &
      row %>% pull(`Braille/tactile signage?`) == 'yes'
    ) {
      paste0('There *is* Braille/tactile signage. ', row %>% pull(`Braille Description`))
    } else {
      paste0('There is *not* Braille/tactile signage in this building.')
    }
  )
  # TODO:
    # Inaccessible spaces: ${inaccess}
    # If yes, describe these: ${inaccess_notes}
    # How are the hallways lit? ${light_type}
    # Describe the lighting: ${light_note}
    # Chemicals and allergens? ${chemical}
  
  say('### Building Features')
  
  number_of_floors <- row %>% pull(`Number of floors`)
  if(!is.na(number_of_floors)) {
    say('- There are ', number_of_floors, ' floors in the building.')
  }
  
  # TODO:
    # ${stairwells} stairwells
    # ${elevators} elevators
    # ${acc_bath} accessible bathrooms
    # ${gn_bath} gender-neutral bathrooms
    # ${gn_acc_bath} accessible gender-neutral bathrooms
    # ${total_bath} total bathrooms
    # Are there any lactation spaces? ${lactation} 
    # Are there prayer or meditation spaces? ${prayer}
  
  say('### Additional information')
  
  say(row %>% pull(`Comments and additional information`))
  
  # attachment_json_for_building <- GET(
  #   paste0(
  #     base_attachment_url,
  #     row %>% pull(`ObjectID`),
  #     "/attachments"),
  #   query = list(
  #     # globalIds = row %>% pull(`GlobalID`),
  #     f = 'pjson'
  #   )
  # )
  
  # parsed_attachment_json <- fromJSON(content(attachment_json_for_building))
  # 
  # if (
  #   (
  #     (
  #       is.null(parsed_attachment_json$error$code) ||
  #       parsed_attachment_json$error$code != 400) &
  #     !(
  #       is.null(parsed_attachment_json$attachmentInfos) ||
  #       length(parsed_attachment_json$attachmentInfos) == 0
  #     )
  #   )
  # ) {  # If there *are* attachments...
  #   for (attachment_row_number in 1:nrow(parsed_attachment_json$attachmentInfos)) {
  #     attachment_row <- parsed_attachment_json$attachmentInfos %>% slice(attachment_row_number)
  #     if (attachment_row$contentType %>% startsWith('image')) {
  #       say('![Image of building](', 'https://services3.arcgis.com/9nfxWATFamVUTTGb/ArcGIS/rest/services/service_12179aa8762647dba17ff539184807a7/FeatureServer/0/15/attachments/', attachment_row$id, ')')
  #     } else {
  #       say('[Link to attachment](', 'https://services3.arcgis.com/9nfxWATFamVUTTGb/ArcGIS/rest/services/service_12179aa8762647dba17ff539184807a7/FeatureServer/0/15/attachments/', attachment_row$id, ')')
  #     }
  #   }
  # }
  
}  # End of for loop
```

```{r notes about the ArcGIS API}
# Audio notes and other attachments:
# Works for getting attachment json for a given Global ID:
# https://services3.arcgis.com/9nfxWATFamVUTTGb/arcgis/rest/services/service_12179aa8762647dba17ff539184807a7/FeatureServer/0/queryAttachments?objectIds=&globalIds=be47a8fd-a98c-4088-9850-b9fb38549538&definitionExpression=&attachmentTypes=&size=&keywords=&resultOffset=&resultRecordCount=&f=pjson

# An actual image location is of this format:
# https://services3.arcgis.com/9nfxWATFamVUTTGb/ArcGIS/rest/services/service_12179aa8762647dba17ff539184807a7/FeatureServer/0/15/attachments/7

# Thus, in the json above, for each attachment, you'd get attachmentGroups -> attachmentInfos -> id. That ID is the end of the image URL above.
# And attachmentGroups -> attachmentInfos -> contentType says, e.g., 'image/jpeg' (vs. audio of some sort).
```

```{r get attachments for an object}

```

![This is alt text for an image](https://services3.arcgis.com/9nfxWATFamVUTTGb/ArcGIS/rest/services/service_12179aa8762647dba17ff539184807a7/FeatureServer/0/15/attachments/7)
