---
title: 'Summary of Space Accessiblity'
author: 'R Group'
date: '`r format(Sys.Date(), format="%B %d, %Y")`'
lang: 'en'
output: 
  html_document:
    keep_md: true
    self_contained: false
params: 
  output_dir: 'output'
---

<!-- This can be viewed, e.g., at 
https://rawgit.com/publicus/upenn-accessible-spaces-dynamic-report/master/Example.html
-->

# TODO

- Finish writing the document
- Only retaining the raw HTML for the body section of the document

## Stretch goals

- API Access to ArcGIS dataset

### Secondary stretch goals

- Using WordPress API to update a post?
  - E.g., `http://web.sas.upenn.edu/access-map/wp-json/wp/v2/pages/` works for *reading* pages Not sure about updating pages yet, though a `PUT` command should work for it.

```{r setup, include=FALSE}
library('dplyr')
library('httr')
library('jsonlite')
library('knitr')
library('readr')

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = TRUE)
knitr::opts_chunk$set(results = 'asis')
```

```{r load data}
dataset <- readr::read_csv("building_inter_4-2-18_FIXED_FIRST_STRING.csv")
```

```{r include=TRUE}
cat("Test")
```

## Summary

We have compiled data on `r dataset %>% nrow()` buildings in this document. Below, you will find information on each building individually.

```{r how many inacessible spaces are there}
inaccessible_spaces <- dataset %>% filter(`Inaccessible spaces` == 'yes')
```

Overall, `r inaccessible_spaces %>% nrow()` (that is, `r ((inaccessible_spaces %>% nrow()) / (dataset %>% nrow()) * 100) %>% round(2)`%) of the `r dataset %>% nrow()` buildings in the dataset contain inaccessible spaces.

```{r loop through buildings}
say <- function(..., space_separator = '\n\n') {
  cat(space_separator, ..., sep = '', collapse = '')
}

for (row_number in 1:nrow(dataset)) {
  row <- dataset %>% slice(row_number)
  
  say('## Building Name: ', row %>% pull(`Building name`))
  say('### Building Information')
  
  say('- Building location (GPS coordinates): ', row %>% pull(x), ", ", row %>% pull(y))
  
  say(
    '- Braille/tactile signage: ',
    if (
      is.na(row %>% pull(`Braille/tactile signage?`))
    ) {
      paste('(Unknown)')
    } else if (
      row %>% pull(`Braille/tactile signage?`) == 'yes'
    ) {
      paste(
        'There *is* Braille/tactile signage:',
        row %>% pull(`Braille Description`)
      )
    } else {
      paste('There is *not* Braille/tactile signage in this building.')
    }
  )
  # TODO:
    # Inaccessible spaces: inaccess
    # If yes, describe these: inaccess_notes
    # How are the hallways lit? light_type
    # Describe the lighting: light_note
    # Chemicals and allergens? chemical
  
  say('### Building Features')
  
  number_of_floors <- row %>% pull(`Number of floors`)
  if (!is.na(number_of_floors)) {
    say('- There are ', number_of_floors, ' floors in the building.')
  }
  
  # TODO:
    # stairwells: stairwells
    # elevators: elevators
    # acc_bath: accessible bathrooms
    # gn_bath: gender-neutral bathrooms
    # gn_acc_bath: accessible gender-neutral bathrooms
    # total_bath: total bathrooms
    # lactation: Are there any lactation spaces? 
    # prayer: Are there prayer or meditation spaces?
  
  say('### Additional information')
  
  say(row %>% pull(`Comments and additional information`))
}  # End of for loop
```
